Bathtub Qualitative Reasoning

### 2016-10-21 paper.tex

            add s to processing\_list
        }
        add s as child to processing\_state
    }
}
\caption{Computing the state-graph based on given an starting state. It starts with a given starting state in the processing list, then it computes all the successors of this state and adds all the succesors as children to state that is being processed, as well as adding these succesors to the processing list, but only if a successor was not already processed.}
\label{alg:computing_state_graph}
\end{algorithm}

>>>>

            add s to processing\_list
        }
        add s as child to processing\_state
    }
}
\caption{Computing the state-graph based on given an starting state. It starts with a given starting state in the processing list, then it computes all the successors of this state and adds all the successors as children to state that is being processed, as well as adding these successors to the processing list, but only if a successor was not already processed.}
\label{alg:computing_state_graph}
\end{algorithm}
